---
title: "PA1HW"
output: html_document
---

Loading and preprocessing the data

```{r,echo=TRUE}
file<-read.csv('activity.csv')##read the data
file2<-aggregate(steps ~ date, data=file, mean)##process the data
```


Make a histogram of the total number of steps taken each day
Calculate and report the mean and median total number of steps taken per day
```{r,echo=TRUE}
hist(file2)##make a histgram
mean(file2[[2]])##find out the mean
median(file2[[2]])##find out the median
```

Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
Below, 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps
```{r,echo=TRUE}
file3<-aggregate(steps ~., data=file,mean)##process the data
file4<-subset(file3,file3[[2]]==5) ##select the interval=5
plot(file4[[3]]~file4[[1]],type="l") ##plot the thing
maxV<-max(file4[3]) ##file the max for interval=5
subset(file4,file4[3]==maxV) ##choose the date for the max value for interval =5
```

Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

I replaced the missing values with the average interpolated from the non-missing values

Create a new dataset that is equal to the original dataset but with the missing data filled in.

The mean from the new data set is the same with the original one, but the median changes with slightly increment from that in original data set.
```{r,echo=TRUE}
file3<-aggregate(steps ~., data=file,mean)##process the data
file4<-subset(file3,file3[[2]]==5) ##select the interval=5
plot(file4[[3]]~file4[[1]],type="l") ##plot the thing
maxV<-max(file4[3]) ##file the max for interval=5
subset(file4,file4[3]==maxV) ##choose the date for the max value for interval =5
```
